Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Working on the parametric and nonpar correction figures.

```{r fig.width=12, fig.height=6}
nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         # Corrected = log_theta_stars - theta,
         Corrected = theta_bar - theta,) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  # filter(., thresh_tests < 500) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
  theme_bw()

>>>>

```{r fig.width=12, fig.height=6}

lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")

nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
         samp_n_tests = factor(samp_n_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Nonparametric") +
  theme_bw()

```{r fig.width=12, fig.height=6}

lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")

par_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
         samp_n_tests = factor(samp_n_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Parametric") +
  theme_bw()
